Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2022-03-13 paper/admin/nhb_cover_letter.tex
updated cover letters and formatting

\greetto{To the editors of \textit{eLife}:}

@@

\begin{document}
\begin{newlfm}
We have enclosed our manuscript entitled \textit{Fitness tracking
  reveals task-specific associations between memory, mental health,
  and exercise} to be considered for publication as a
\textit{Research Article}.  The manuscript reports new evidence that, just as different
forms of exercise affect \textit{physical} health in different ways,
different forms of exercise also affect cognitive performance and
mental health differently.

@@

Thank you for considering our manuscript, and we hope you will find it suitable for publication in \textit{eLife}.

>>>>

\greetto{To the editors of \textit{Nature Human Behavior}:}

@@

\begin{document}
\begin{newlfm}
We have enclosed our manuscript entitled \textit{Fitness tracking
  reveals task-specific associations between memory, mental health,
  and exercise} to be considered for publication as an
\textit{Article}.  The manuscript reports new evidence that, just as different
forms of exercise affect \textit{physical} health in different ways,
different forms of exercise also affect cognitive performance and
mental health differently.

@@

Thank you for considering our manuscript, and we hope you will find it
suitable for publication in \textit{Nature Human Behavior}.

### 2022-03-13 paper/admin/science_advances_cover_letter.tex
updated cover letters and formatting

\greetto{To the editors of \textit{Nature Human Behavior}:}

@@

\begin{document}
\begin{newlfm}
We have enclosed our manuscript entitled \textit{Fitness tracking
  reveals task-specific associations between memory, mental health,
  and exercise} to be considered for publication as an
\textit{Article}.  The manuscript reports new evidence that, just as different
forms of exercise affect \textit{physical} health in different ways,
different forms of exercise also affect cognitive performance and
mental health differently.

@@

Thank you for considering our manuscript, and we hope you will find it
suitable for publication in \textit{Nature Human Behavior}.

>>>>

\greetto{To the editors of \textit{Science Advances}:}

@@

\begin{document}
\begin{newlfm}
We have enclosed our manuscript entitled \textit{Fitness tracking
  reveals task-specific associations between memory, mental health,
  and exercise} to be considered for publication as an
\textit{Research Article}.  The manuscript reports new evidence that, just as different
forms of exercise affect \textit{physical} health in different ways,
different forms of exercise also affect cognitive performance and
mental health differently.

@@

Thank you for considering our manuscript, and we hope you will find it
suitable for publication in \textit{Science Advances}.

### 2022-03-13 paper/admin/scientific_reports_cover_letter.tex
updated cover letters and formatting

\greetto{To the editors of \textit{Science Advances}:}

@@

\begin{document}
\begin{newlfm}
We have enclosed our manuscript entitled \textit{Fitness tracking
  reveals task-specific associations between memory, mental health,
  and exercise} to be considered for publication as an
\textit{Research Article}.  The manuscript reports new evidence that, just as different
forms of exercise affect \textit{physical} health in different ways,
different forms of exercise also affect cognitive performance and
mental health differently.

@@

Thank you for considering our manuscript, and we hope you will find it
suitable for publication in \textit{Science Advances}.

>>>>

\greetto{To the editors of \textit{Scientific Reports}:}

@@

\begin{document}
\begin{newlfm}
We have enclosed our manuscript entitled \textit{Fitness tracking
  reveals task-specific associations between memory, mental health,
  and exercise} to be considered for publication in \textit{Scientific
  Reports}.  The manuscript reports new evidence that, just as different
forms of exercise affect \textit{physical} health in different ways,
different forms of exercise also affect cognitive performance and
mental health differently.

@@

Thank you for considering our manuscript, and we hope you will find it
suitable for publication in \textit{Scientific Reports}.

### 2022-03-13 paper/main.tex
updated cover letters and formatting

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[sort]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{authblk}

@@

For their participation, workers received a base payment of \$5 per hour (computed in 15
minute increments, rounded up to the nearest 15 minutes), plus an
additional performance-based bonus of up to \$5.  Our recruitment
procedure and study protocol
were approved by Dartmouth's Committee for the Protection of Human Subjects.

@@

We wondered about potential links between the different aspects of
participants' data.  For example, if people who exercised in a
particular way also tended to perform better on a given memory task,
this could suggest that either (a) some property intrinsic to participants who
exercised in a particular way might also affect their memory
performance on the given task, and/or (b) particular exercise behaviors
could have a causal impact on memory performance.  We carried out an
exploratory analysis whereby we used a bootstrap-based approach (see
\textit{Exploratory correlation analyses}) to
identify reliable correlations between different aspects of memory
performance (Fig.~\behBehCorr), different aspects of fitness (Fig.~\fitFitCorr), different demographic
attributes (Fig.~\demDemCorr), and correlations between memory
performance, fitness information, and demographic attributes
(Fig.~\allCorr).  Several patterns emerged.  First, we found that
participants' performance on the (within-task) immediate versus delayed memory tests
from the free recall, naturalistic recall, and foreign language
flashcards tasks were positively correlated ($r$s $> 0.25$, $p$s $< 0.003$).  This suggests that, within each of these tasks,
similar processes or constraints may influence both short term and
long term information retrieval.  We also found reliable across-task correlations
between participants' (immediate and delayed) performance on the free
recall and foreign language flashcards tasks ($r$s $> 0.3$, $p$s $< 0.03$).

@@

\section*{Acknowledgements}
We acknowledge useful discussions with David Bucci, Emily Glasser,
Andrew Heusser, Abigail Bartolome, Lorie Loeb, Lucy Owen, and Kirsten
Ziman.  Our work was supported in part by the Dartmouth Young Minds
and Brains initiative.  The content is solely the responsibility of
the authors and does not necessarily represent the official views of
our supporting organizations.  This paper is dedicated to the memory
of David Bucci, who helped to inspire the theoretical foundations of
this work.  Dave served as a mentor and colleague on the project prior
to his passing.

>>>>

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[sort, numbers]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{authblk}

@@

For their participation, workers received a base payment of \$5 per
hour (computed in 15 minute increments, rounded up to the nearest 15
minutes), plus an additional performance-based bonus of up to \$5.
Our recruitment procedure and study protocol were approved by
Dartmouth's Committee for the Protection of Human Subjects.  We
obtained informed consent using an online form administered to all
prospective participants prior to enrolling them in our study.  All
methods were performed in accordance with the relevant guidelines and
regulations.

@@

We wondered about potential links between the different aspects of
participants' data.  For example, if people who exercised in a
particular way also tended to perform better on a given memory task,
this could suggest that either (a) some property intrinsic to
participants who exercised in a particular way might also affect their
memory performance on the given task, and/or (b) particular exercise
behaviors could have a causal impact on memory performance.  We
carried out an exploratory analysis whereby we used a bootstrap-based
approach to identify reliable correlations between different aspects
of memory performance (Fig.~\behBehCorr), different aspects of fitness
(Fig.~\fitFitCorr), different demographic attributes
(Fig.~\demDemCorr), and correlations between memory performance,
fitness information, and demographic attributes (Fig.~\allCorr).
Specifically, we sought to identify correlations that were present in
the same direction (i.e., positive or negative) across different
subsets of participants.  For each test, we report the average correlation (taken
across 10,000 subsets of participants, chosen with replacement) and
an associated two-tailed $p$-value, estimated as
\[
p = 2 \times (1 - q),
\]
where $q$ is the proportion of those
10,000 subsets that exhibited correlations in the same direction  (see
\textit{Exploratory correlation analyses}).  When all 10,000 randomly
chosen subsets of participants exhibited correlations in the same
direction (i.e., all positive correlations or all negative
correlations), we report the $p$-value as $p < 0.0001$.

Several patterns emerged from these analyses.  First, we found that
participants' performance on the (within-task) immediate versus delayed memory tests
from the free recall, naturalistic recall, and foreign language
flashcards tasks were positively correlated ($r$s $> 0.25$, $p$s $< 0.003$).  This suggests that, within each of these tasks,
similar processes or constraints may influence both short term and
long term information retrieval.  We also found reliable across-task correlations
between participants' (immediate and delayed) performance on the free
recall and foreign language flashcards tasks ($r$s $> 0.3$, $p$s $< 0.03$).

@@

\section*{Acknowledgements}
We acknowledge useful discussions with David Bucci, Emily Glasser,
Andrew Heusser, Abigail Bartolome, Lorie Loeb, Lucy Owen, and Kirsten
Ziman.  Our work was supported in part by the Dartmouth Young Minds
and Brains initiative, and by NSF grant number 2145172 to J.R.M.  The
content is solely the responsibility of the authors and does not
necessarily represent the official views of our supporting
organizations.  This paper is dedicated to the memory of David Bucci,
who helped to inspire the theoretical foundations of this work.  Dave
served as a mentor and colleague on the project prior to his passing.
